---
title: "CodeBook"
author: "Mael Elegoet"
date: "2023-01-12"
output: html_document
---



## CodeBook for Getting and cleaning data final assignment


The fisrt task in this assignment was to understand the datas and metadatas and how their were linked together.
It wasn't really difficult, but they were no too much info ;)
I just had to take some time.

In my zero Step I made all the preparatory work loading all datasets.
Each dataset was made of 561 variables which were all discribed in the features.txt file.

In first step, first of all I made complete datasets both for test sample and for training sample.
I wanted to have complete datasets with all variables from the begining of the work.
so I merged records, activity codes and subject identifier from the three sources (X_test the raw data file, y_test the activity label corresponding to each record of X_test and finally subject_test which was the subject identifier for also each row in X_test).
The correspondance was line to line so I had just to use cbind().

I did the same operations with the training sample.

Finally I merged the two datasets (test and training) whom had exactly the same columns. So rbind() was good for this treatment.

I then went to step 4 because I wanted all my columns to have clear names in my dataset.

Then I selected only the columns with mean or standard deviation (std) in their title as it was asked at step 2.
I used the dplyr command select with match function from base r. Plus, I kept the activity code and subject identifier from step 1.

Finally I used a left join to add the activity labels to the light dataframe obtained at previous step. This was asked in step 3.

Lastly I used the group_by command from dplyr package in order to summarize the dataset by subject and activity with the mean for each variable.

That is.

```{r data load}
load("df_light.Rda")
load("df_summary.Rda")

```



* Names of the variables in the clean dataset
```{r df_light names}

colnames(df_light)


```


* Names of the variables in the summary of the dataset

```{r df_summary names}
colnames(df_summary)

```

